\documentclass[12pt,a4paper]{report}

\usepackage[T1]{fontenc} % Latin Extended font
\usepackage{ebgaramond} % EB Garamond font
\usepackage{tgheros}    % TeX Gyre Heros font
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % American English
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % formatting of date 
\usepackage{tabto}    % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing
\usepackage{calc} % paragraphs alignment
\usepackage[maxcitenames=6, minnames=3 ]{biblatex}
\addbibresource[]{biblio.bib}

\newcommand{\myname}{CY Chingyao Fu}
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

\newcommand{\listtabwidth}{1.7cm}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % Pitch 0.03em
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

\geometry{body={16.5cm, 22.8cm}, % set page margins
    left=2.5cm,
    top=3cm}

\setlength\parindent{0em} % no indentation

\setstretch{0.95} % set line spacing

\newcommand{\listitemspace}{0.25em} % define space between list items

\renewenvironment{itemize} % no bullets
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% set table format
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year 
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {Semiconductor, System, PM, Project Management, Product Management},
    pdftitle    = {\myname: Chingyao Fu},
    pdfsubject  = {Chingyao Fu},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright{}

    \namefont{\myname}

    \vspace{1em}
    \begin{minipage}[t]{0.7\textwidth}
        Senior Director of Product Management,\\
        Smart Vehicle Division (SVD),\\
        Industrial Automotive Business Group (IABG),\\
        Wistron Corporation
    \end{minipage}
    \begin{minipage}[t]{0.295\textwidth}
        \flushright{}
        NTUT\ 111C51502\\
        \href{mailto:fu402138670@gmail.com}{fu402138670@gmail.com} \\
        +886 983 678 013 \\
        \href{https://orcid.org/0009-0004-9005-5183}
        {orcid 0009-0004-9005-5183}
    \end{minipage}
    \vspace{1em}
    \hrule
    
    \section*{Professional profile}
        \begin{tablist}
        \item Entrepreneurship and execution oriented. 
        \item Well-know the manufacturing, engineering, and market challenges. 
        \item 3 years’ entrepreneurial experience for handheld NIR detecting equipment. 
        \item 23 years of experience in the design, manufacturing and marketing of IC and electronic products. 
        \end{tablist}
    
    \section*{Education}
    
    \begin{tablist}
      \item[M.S.] \tab{}EECS, National Taipei University of Technology, Taipei, TAIWAN, 2022-Now
      \item[M.S.] \tab{}EMBA, The University of Texas at Arlington, Texas, USA, 2022-Now
      \item[M.S.] \tab{}MEE, Chung Hua University, Hsinchu, TAIWAN, 1994-1996
      \item[A.D.] \tab{}EE, Ming Hsin Junior College, Hsinchu, TAIWAN, 1986-1991
    \end{tablist}

    \section*{Service}
    \subsection*{Senior Director of Product Management, Wistron, Oct 2019 - Now}
    \begin{itemize}
        \item UAV(drone) Product Line Management
        \item Commercial EV Product Line Management
        \item Acoustic Product Line Management (Before Dec 2021)
    \end{itemize}
    \subsection*{Senior Manager of Product and Business Development, Foxconn, Apr 2017 - Sep 2019}
    \begin{itemize}
        \item Belkin Linksys Networking Product China SMB Sales Management
        \item Implement Smart Home Ecosystem To China Market
        \item Build Up Smart Camera, Smart Mesh Gateway, Smart Speaker Product Lines.
    \end{itemize}
    \subsection*{GM And Founder, Magispec Technology, Apr 2015 - Apr 2017}
    \begin{itemize}
        \item Lead And Managed An Entrepreneurial Team.
        \item Developed A Low Cost NIR Milk Analyzer For China Market 
        \item Developed A Portable Fast Drug Detector By NIR spectrum Technology For Police Department .
    \end{itemize}
    \subsection*{Senior Manager of Product Management, Foxconn, Apr 2010 - Apr 2015}
    \begin{itemize}
        \item Apple WiFi Module Business Management. 
        \item China(Xiaomi, Baidu, Alibaba, Lenovo) Market Business Management.
        \item OTT and WiFi Router Related Product Lines Management.
    \end{itemize}
    \subsection*{Engineering, RD, Sales Manager of PKG BU, Foxconn, Feb 1999 - Apr 2010}
    \begin{itemize}
        \item RF Modules, WiFi Modules, Optical Modules Business Management. 
        \item Build Up ISO9000 And QS9000 Procedures.
        \item Build Up Engineering And RD Teams.
    \end{itemize}
    \subsection*{Product And Testing Section Manager, MOST Semiconductor, Jun 1996 - Feb 1999}
    \begin{itemize}
        \item Process Engineer For Photo-coupler And MMIC. 
        \item RF Testing Engineer For MMIC.
        \item Trained in NEC, Japan.
    \end{itemize}

    \section*{Certificates And Awards}
    \begin{tablist}
        \item[2010] \tab{}Year Excellent Manager of Hon-Hai Precision Co. Ltd.
        \item[2003] \tab{}6 Sigma Green-belt 
        \item[1997] \tab{}Taiwan Radioactive Materials or Ionizing Radiation Equipment Operating License
    \end{tablist}

    \section*{Publications}
    \begin{tablist}
        \item[TW201123869A] \tab{} Camera module and method of manufacturing same
        \item[TW201103114A] \tab{} Flat chip package structure and method thereof
        \item[TW201042749A] \tab{} Integrated package assembly
        \item[TW201039424A] \tab{} Method and assembly of welding flip chip on a substrate
        \item[TW201039413A] \tab{} Chip package assembly and substrate processing method thereof 
        \item[TW201036115A] \tab{} Assembly and method of chip package
        \item[TW201032687A] \tab{} Method for levelling surface of LGA substrate
        \item[TW200947632A] \tab{} Semiconductor package structure and method same
        \item[CN107280679A] \tab{} Intelligent infant monitoring care system and operation method thereof
        \item[CN107280561A] \tab{} Infant intelligent toilet seat and intelligent toilet seat system
        \item[CN102045494A] \tab{} Camera module and making method thereof
        \item[CN101937886A] \tab{} Thin chip package structure and method
        \item[CN101894829A] \tab{} Stacked encapsulating structure
        \item[CN101872727A] \tab{} Chip welding method and structure
        \item[CN101866886A] \tab{} Chip packaging structure and substrate processing method thereof
        \item[CN101834162A] \tab{} Chip packaging structure and method
        \item[CN101826468A] \tab{} Method for manufacturing substrate
        \item[CN101937886B] \tab{} Thin chip package structure and method
        \item[CN101894829B] \tab{} Stacked encapsulating structure
        %\item[1996] \tab{}\tab{} Techniques for designing the macro model of switched reluctance motor and its controller with SPICE, Chung Hua University
    \end{tablist}

    \section*{Skills}
    \begin{tablist}
        \item[Hardware] \tab{}IC Package, SMT, System Assembly, Testing And Failure Analysis Equipment 
        \item[Software] \tab{}\tab{}Python, C, Java, LaTex
        \item[Mechanical] \tab{}ProE, AutoCad
        \item[Design/Simulation] \tab{}PSpice, Protel, Allego, Matlab, Illustrator, Keyshot, ArduPilot
    \end{tablist}

\end{document}